---
title: "Activity: Nuclear Reactors"
author: "Mia Iceland"
output: html_notebook
---

```{r}
library(tidyverse)
library(rvest)
library(dplyr)

```

## Scrape the Data 

```{r}
#My code here.... 

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"

ListofTables <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

Japan1 <- ListofTables[[21]]

```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

The columns which are tidy are "Plantname", "Type", and "Capacity". "Model" and "Status" are not tidy because there are extra notes within certain cells of data. Also, "Beginbuilding" and "Commercialoperation" have multiple types of dates (month, day, and year) in only one cell. Finally, "Closed" has missing data. 


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 

Japan2 <-
  Japan1 %>%
  select(1:9) %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed)

Japan3 <-
  Japan2 %>%
    mutate(Reactor = as.numeric(reactor),
           NetMW = as.numeric(netMW),
           Construction = lubridate::dmy(construction),
           Operation = lubridate::dmy(operation),
           Closure = lubridate::dmy(closure)
           )

Japan <-
  Japan3 %>%
    mutate(Country = "Japan") %>%
    select(Country, name, Type, model, status, Reactor, NetMW, Construction, Operation, Closure)

Japan %>%
  ggplot(aes(x= Construction, y= NetMW, color= Type)) +
  geom_point()

```

## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 

China1 <- ListofTables[[10]]

China2 <-
  China1 %>%
  select(1:9) %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed)

China3 <-
  China2 %>%
    mutate(Reactor = as.numeric(reactor),
           NetMW = as.numeric(netMW),
           Construction = lubridate::dmy(construction),
           Operation = lubridate::dmy(operation),
           Closure = lubridate::dmy(closure)
           )

China <-
  China3 %>%
    mutate(Country = "China") %>%
    select(Country, name, Type, model, status, Reactor, NetMW, Construction, Operation, Closure)

NewTable <-
  bind_rows(Japan, China)

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here

```